Observation of the Torsional Motion of a Solar Jet at the Limb

### 2016-08-14 paper/ms_temp_paper.tex
Abstract last discussion and evolution

\title{Solar jet observed at the limb in SDO/SST}
\author{S.M.Bennett$^1$
A.J.Leonard$^1$
\and R. Erd{\'e}lyi$^{1,2}$}
\affil{$^1$ Solar Physics and Space Plasma Research Centre (SP2RC), University of Sheffield, Hicks Building, Hounsfield Rd, S3 7RH, UK}
\affil{$^2$ Debrecen Heliophysical Observatory (DHO), Research Centre for Astronomy and Earth Sciences, Hungarian Academy of Sciences, 4010 Debrecen, P.O. Box 30, Hungary}

\begin{abstract}
\end{abstract}

@@

%double check this section
Evidently, the maximum extent of this feature is in SDO $30.4$ and maximises at $12.6$ Mm although the measurements in H$\alpha$ may exceed this were it to be fully visible.
Interestingly, the length of the jet in the coronal lines does not get larger after the second injection on plasma occurs.
This subsequent acceleration of plasma originates from the same location as that of the initial formation, and on the same scale as the first onset.
However, this drives the tip of the jet even higher than the initial.

% need much more here

@@

\begin{pycode}[SST_slit]
from __future__ import print_function
import numpy as np
import sunpy.cm
import matplotlib.pyplot as plt
from astropy.visualization.mpl_normalize import ImageNormalize 
from astropy import visualization

norm=ImageNormalize(stretch=visualization.AsinhStretch(1))

sst_slit_path = manager.data_file('2016-01-22 14:59:58.507931.npz')

afile = np.load(sst_slit_path)
data = afile['arr_2']

fig = plt.figure(figsize=texfigure.figsize(pytex, figure_width_context='textwidth'))
plt.imshow(np.rot90(data[2])[::-1, 100:], cmap='viridis', aspect='auto', origin='lower', norm=norm)
plt.colorbar()
plt.xlabel('Time in SST cadence (7.7 s)')
plt.ylabel('Distance along the slit')
sst_slit_fig = manager.save_figure('sst-slit', fig)
sst_slit_fig.figure_env_name = r'figure*'
sst_slit_fig.figure_width = r'\textwidth'
sst_slit_fig.placement = 't'
sst_slit_fig.caption = r'CRISP/SST H$\alpha$ core line slit analysis.'

print(sst_slit_fig.repr_figure(), file=sys.stderr)
\end{pycode}

\py[SST_slit]|sst_slit_fig|

@@

% this section needs rewriting
The velocity values given here are slow compared to those presented in previous works, however, we believe these to be accurate, and attribute this to the smalls scale of the initial loop.
A wider loop would produce a greater radius for the plasma to rotate around, and therefore a greater angular velocity.% some questionable physics going on here

@@

The feature is also visible in higher coronal lines, however it does appear just below the solar limb as

>>>>

\title{Observation of the Torsional Motion of a Solar Jet at the Limb}
\author{S.M.Bennett$^1$
A.J.Leonard$^1$
\and R. Erd{\'e}lyi$^{1,2}$}
\affil{$^1$ Solar Physics and Space Plasma Research Centre (SP2RC), University of Sheffield, Hicks Building, Hounsfield Rd, S3 7RH, UK}
\affil{$^2$ Debrecen Heliophysical Observatory (DHO), Research Centre for Astronomy and Earth Sciences, Hungarian Academy of Sciences, 4010 Debrecen, P.O. Box 30, Hungary}

\begin{abstract}
We present observations of a jet event measured by multiple instruments on the $21$st of June $2012$ at the eastern solar limb.
Utilising CRISP at the Swedish Solar Telescope (SST), the Atmospheric Imaging Assembly (AIA) on-board the Solar Dynamic Observatory (SDO) and the alternate view given by STEREO-A's EUVI instrument.
We closely examine the evolution of the jet in extreme detail using CRISP and on a more global scale using the range of wavelengths available on AIA.
The feature is clearly visible in the chromospheric lines of H$\alpha$ and He II $30.4$ nm, however, visibility does decrease as observations move up the corona.
The jet extends to $12.6$ in length and follows the standard jet formation model.
We develop a new method for the calculation of dopplergrams using the MCMC fitting method to adapt to the problems of multiple forms of emmision absorption lines at the limb.
This reveals that the jet rotates first one way and then the other as a result of the unwinding of twist inherent in the emerging bipole.

\end{abstract}

@@

%double check this section
Evidently, the maximum extent of this feature is in SDO $30.4$ and maximises at $12.6$ Mm although the measurements in H$\alpha$ may exceed this were it to be fully visible.
Interestingly, the length of the jet in the coronal lines does not get larger after the second injection on plasma occurs.
This subsequent acceleration of plasma originates from the same location as that of the initial formation, and on the same scale as the first onset.
However, this drives the tip of the jet even higher than the initial tip, measuring the velocity accurately is difficult, due to this acceleration is set against the previous bright material.
An approximation using multiple image steps and using a difference delta produces an average of $46$ kms{^{-1}}, therefore we can infer that it reaches a higher maximum velocity than the first ejection.

The feature is very thin, averaging $1.13$ Mm in H$\alpha$ and $0.787$ Mm in He II. 
This result is unexpected, it certainly seems to contradict the cool core surrounded by a hot sheath model.
However the errors on the measurement in SDO/AIA recordings are $\pm1.5$ Mm, when taking into account human measurement error and resolution of the instrument.
Where as measurement error on the CRISP/SST images is $\pm0.0885$ Mm, thus, we are more inclined to believe the measurement according to CRISP.

@@

%\begin{pycode}[SST_slit]
%from __future__ import print_function
%import numpy as np
%import sunpy.cm
%import matplotlib.pyplot as plt
%from astropy.visualization.mpl_normalize import ImageNormalize 
%from astropy import visualization
%
%norm=ImageNormalize(stretch=visualization.AsinhStretch(1))
%
%sst_slit_path = manager.data_file('2016-01-22 14:59:58.507931.npz')
%
%afile = np.load(sst_slit_path)
%data = afile['arr_2']
%
%fig = plt.figure(figsize=texfigure.figsize(pytex, figure_width_context='textwidth'))
%plt.imshow(np.rot90(data[2])[::-1, 100:], cmap='viridis', aspect='auto', origin='lower', norm=norm)
%plt.colorbar()
%plt.xlabel('Time in SST cadence (7.7 s)')
%plt.ylabel('Distance along the slit')
%sst_slit_fig = manager.save_figure('sst-slit', fig)
%sst_slit_fig.figure_env_name = r'figure*'
%sst_slit_fig.figure_width = r'\textwidth'
%sst_slit_fig.placement = 't'
%sst_slit_fig.caption = r'CRISP/SST H$\alpha$ core line slit analysis.'
%
%print(sst_slit_fig.repr_figure(), file=sys.stderr)
%\end{pycode}
%
%\py[SST_slit]|sst_slit_fig|

@@

% this section needs rewriting
The velocity values given here are slow compared to those presented in previous works, however, we believe these to be accurate, and attribute this to the smalls scale of the initial loop.
A larger scale loop would mean that the magnetic tension would be greater, and hence, experience greater restoring force, inducing higher velocities.

@@

The spectroscopic readings, as show in \cref{dop_shift_sect}, demonstrates a small, but appreciable perturbation in the rotational velocity of the jet like feature.
We find that the jet exhibits a torsional behaviour, demonstrating shifts indicating rotation in one direction and then the other.
The magnitude of these velocities is, however, low.
we conclude that this is a result of the very small source loop of the feature, although this of course needs further enquiry.

With respect to the features affect on the atmosphere, we find a boundary interaction between the jet and atmosphere in the H$\alpha$ images.
This interaction has manifested as dark streaks at the every edges of the feature during the same phase in which the second event causes the acceleration of further plasma.
It is also the phase in which we observe the torsional rotation of the jet.
Whether these dark streaks are physically significant we cannot comment upon too confidently at this time, but they appear at the same time as the second acceleration and the onset of rotational behaviour, cannot merely be coincidence.
